CASTRO: A New Compressible Astrophysical Solver. IV. Performance Portability

### 2019-03-22 gpus/paper.tex
update with BCs
lots of paper refs

With GPU accelerators becoming increasingly dominant, algorithms need to be ported.
There are a number of descriptions of GPU-enabled astrophysical hydro codes, including
\citet{gamer,cholla,fargo3d,pekkila:2017,caplan:2018,racz:2018,liska:2018,goz:2018}

@@

Disucss changes since last paper

@@

>>>>

With GPU accelerators becoming increasingly dominant, algorithms need to be ported.
There are a number of descriptions of GPU-enabled astrophysical hydro codes, including
\citet{gamer,cholla,fargo3d,pekkila:2017,caplan:2018,racz:2018,liska:2018,goz:2018,wang:2010} \MarginPar{todo: group by AMR/no-AMR, GPU exclusive, Kokkos, ...}

@@

\castro\ development began with \cite{castro}, with the goal of
creating an astrophysical hydrodynamics code using a modern adaptive
mesh refinement library (BoxLib at the time) and unsplit hydrodynamics
techniques.  The initial application area was nuclear astrophysics,
including core-collapse supernovae, so it was designed to work with a
general equation of state~\cite{zingalekatz} and reaction network, and
with radiation transport (through flux limited diffusion,
\citealt{castro2,castro3}).  \castro\ also acted as the compressible
counterpart to our low Mach number hydrodynamics code \maestro,
sharing much of the same infrastructure, and allowing for simulations
to be restarted from the low Mach regime into the compressible
regime~\cite{malone:2014}.  \castro\ has been applied to various
progenitor models of Type Ia
supernova~\cite{malone:2014,katz:2016,polin:2019}, exoplanet
dynamics~\cite{ryu:2018}, core-collapse and population III
supernovae~\cite{chen:2014,dolence:2015,chen:2017}, and X-ray bursts~\cite{astronum:2018}..

@@

Boundary conditions require special attention---threadblock must include
all zones that participate in the boundary.
